---
title: "Sample Analysis"
author: "Gord Brown"
date: "`r Sys.Date()`"
output: html_document
---

Initial Configuration Data:
```{r base_config,cache=TRUE}
sampleSheet <- "sample_siCt.txt"
plots_dir <- "generated/plots"
if (!file.exists(plots_dir)) {
  dir.create(plots_dir,recursive=TRUE)
}
```

The following section sets up logging, so we can record whatever actions we
take, print out variables, etc.  For a long-running analysis, this can be used
to report progress, or print critical values along the way if results are
coming out strange.
```{r logging_config}
library(logging)
logFile <- "sample_logfile.txt"
logger <- getLogger("sample_logger")
logger$addHandler(writeToFile,file=logFile,level='DEBUG')
logger$setLevel('DEBUG')
```

First load up the data, and print out the first few lines.
```{r load_data,cache=TRUE,dependson="base_config"}
scores <- read.table(sampleSheet,header=TRUE)
dnames <- colnames(scores)
head(scores)
```
We've loaded the data, so now we can report that there are `r ncol(scores)` samples, with `r nrow(scores)` data points per sample.

Now make some correlation scatter plots across the replicates:
```{r make_plots,cache=TRUE,dependson="load_data"}
for (i in 2:ncol(scores)) {
  plot(scores[,1],scores[,i],xlab=dnames[1],ylab=dnames[i])
}
```

And a histogram:
```{r plot_histogram,cache=TRUE,dependson="load_data"}
hist(scores[,1],breaks=30,xlab=dnames[1],main="Peak Scores")
```

Generate some high quality plots in PDF format, for use in manuscripts:
```{r make_quality_plots,cache=TRUE,dependson="load_data"}
for (i in 2:ncol(scores)) {
  filename <- file.path(plots_dir,sprintf("%s_%s_corr.pdf",dnames[1],dnames[i]))
  logger$info(filename)
  pdf(filename)
  plot(scores[,1],scores[,i],xlab=dnames[1],ylab=dnames[i])
  dev.off()
}
```

Always useful to print out the session info at the end of the script, so you
know what you were running at the time.
```{r base_final}
sessionInfo()
```
